Paper

### 2012-02-04 papers/itsc_2012/draft.tex
re-enabled edge trimming with more restraints.. it's at least a bit better

>>>>

interface... what invariants do agents have to follow, and how does the default
behavior provide them?

\section{notes}

possible background/links
http://www.caliper.com/transmodeler/default.htm
http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6082793
 https://www.google.com/search?sourceid=chrome&ie=UTF-8&q=Agent-Based+Traffic+Simulation+and+Traffic+Signal+Timing+Optimization+with+GPU
